\vspace{-1em}\thetitle

### 2009-09-22 paper.tex
...

For our experiments, we use randomly sampled traffic from six network traces.
The traces are freely available from the \caps{CRAWDAD} trace repository~\cite{Yeo06}.
Details of the traces are shown in \Table{traces}.
% These data sets represent a broad cross-section of traffic patterns over time and a reasonable variety of network types.
% Unfortunately, we could not find any freely available residential or corporate network traces that were usable for our analysis.
We randomly sampled 5000 flows from each trace for training and another 5000 flows for testing.
% Since the initial five packets are used for prediction, we consider only flows with at least five packets.
The results are shown in \Figure{accuracy}.
The left panel shows the accuracy rates of predicting packet size and inter-packet interval distributions.
Accuracy is computed by comparing the distribution of Kolmogorov-Smirnov (K-S) test p-values to an empirical ideal distribution of K-S p-values, taking the maximum deviation from the ideal as the error rate.
Since no previous work attempts to either model individual flow behavior or predict flow behavior from initial observations, we compare our prediction technique to two simple and obvious approaches:
predicting the already observed behavior of each flow, and
predicting the average behavior of the training trace.
The right-top panel shows the accuracy rate for predicting which flow will have more packets between random pairs of flows.
Choosing randomly gives 50\% accuracy, which we exceed significantly on all traces.

Our method does not yield perfect predictions, but the non-deterministic nature of flow behavior implies that it is impossible to achieve perfect prediction.
Moreover, we do not know what the inherent upper limit on prediction quality is:
no prior work provides detailed statistical models of individual flow behaviors, nor does any earlier research attempt to predict individual flow behavior from a few initial packets.
The fact that this technique can accurately predict flow behavior from so few initial packet observations is evidence that our hypothesized mixture model for flow behavior has merit.
With improvements in the algorithms used to recover the model parameters, we are confident that even better prediction accuracy can be achieved.
Furthermore, the same model can be applied to traffic classification from flow behavior, and to generation of realistic synthetic network traffic from collections of trace data.
These applications, however useful, are merely pleasant side effects of the real breakthrough of this work:
a detailed statistical model for individual flow behaviors across whole networks.

>>>>

For our experiments, we use randomly sampled traffic from six network traces.
The traces are freely available from the \caps{CRAWDAD} trace repository~\cite{Yeo06}.
Details of the traces are shown in \Table{traces}.
% These data sets represent a broad cross-section of traffic patterns over time and a reasonable variety of network types.
% Unfortunately, we could not find any freely available residential or corporate network traces that were usable for our analysis.
We randomly sampled 5000 flows from each trace for training and another 5000 flows for testing.
% Since the initial five packets are used for prediction, we consider only flows with at least five packets.
The results are shown in \Figure{accuracy}.
The left panel shows accuracy rates for predicting packet size and inter-packet interval distributions.
Since no previous work attempts to either model individual flow behavior or predict flow behavior from initial observations, we compare our prediction technique to two simple and obvious approaches:
predicting the already observed behavior of each flow, and
predicting the average behavior of the training trace.
Accuracy is computed by comparing the distribution of Kolmogorov-Smirnov (K-S) test p-values to an empirical ideal distribution of K-S p-values, taking the maximum deviation from the ideal as the error rate.
The right-top panel shows the accuracy rate for predicting which flow will have more packets between random pairs of flows.
Choosing randomly gives 50\% accuracy, which we exceed significantly on all traces.

Our method does not yield perfect predictions, but the non-deterministic nature of flow behavior implies that it is impossible to achieve perfect prediction.
Moreover, we do not know what the inherent upper limit on prediction quality is.
No prior work has provided detailed statistical models of individual flow behaviors, or attempted to predict individual flow behavior from initial packets.
The fact that this technique can accurately predict flow behavior from so few initial packet observations is evidence that our hypothesized mixture model for flow behavior has merit.
With improvements in the algorithms used to recover the model parameters, we are confident that even better prediction accuracy can be achieved.
Furthermore, the same model can be applied to traffic classification from flow behavior, and to generation of realistic synthetic network traffic from collections of trace data.
These applications, however useful, are merely pleasant side effects of the real breakthrough of this work:
a realistic, detailed statistical model for individual flow behaviors across whole networks.
